\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-30 ase20/conclusion.tex
Till Sec. 7

\section{Conclusion}\label{sec:conclude}

The annual updates of the ECMAScript makes it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed a tool \( \tool \),
which \textit{automatically} extracts the syntax and semantics specified in
ECMAScript.  The tool generates a parser from a language grammar written in \(
\bnfes \), and an AST-IR translator from abstract algorithms written in
English.  The tool automatically extract all syntax and \inred{XX.XX\%} of
semantics for the most recent four versions of ECMAScript (ES7 to ES10).  We
evaluated the correctness of the tool by testing the extracted semantics from
ES10 with Test262, the official conformance suite.  Based on \inred{X,XXX}
failed tests, we found eight specification errors in ES10. After resolving
them, the extracted semantics passed all \inred{XX,XXX} applicable tests.
Moreover, we showed that \( \tool \) is also forward compatible for the future
language features by applying it to nine proposals, and we found four
specification errors in the proposal for BigInt.  We believe that it could
dramatically reduce the human efforts to define formal semantics of ECMAScript
and also bridge gaps between ECMAScript and Test262.

>>>>

\section{Conclusion}\label{sec:conclude}
Annual updates of ECMAScript make it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
that \textit{automatically} extracts the syntax and semantics as a parser and
an AST-IR translator from ECMAScript written in English.
The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
semantics for the most recent four versions of ECMAScript (ES7 to ES10).
We evaluated the correctness of the tool by testing the extracted
semantics from ES10 with Test262, the official conformance suite.
Using \inred{X,XXX} failed tests, we found nine specification errors,
four of which are newly discovered, confirmed by TC39, and planned to
be integrated in ES11.  After fixing the errors, the extracted
semantics passed all \inred{XX,XXX} applicable tests in Test262.
We also showed that \( \tool \) is forward compatible by applying it to nine
proposals to be included in ES11, which let us find four errors in the
BigInt proposal.  We believe that \( \tool \) can dramatically reduce
human efforts in building various JavaScript tools correctly.

### 2020-04-30 ase20/related.tex
Till Sec. 7

From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars (CFGs) even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
does not support context-sensitive features.  Unlike GLL parsing, our lookahead
parsing is applicable for JavaScript parsers having context sensitive features
such as positive/negative lookaheads. Moreover, The complexity of lookahead
parsing is \( O(k \cdot n) \) for the input size \( n \) and the constant
number of tokens \( k \). We experimentally showed that it can generate parsers
for the most recent four versions of ECMAScript.

In the field of automatic model generation, the closest related work to
ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and various heuristic methods,
it produces several candidate code tests them with actual implementation
of the API functions to find correct modeling.  Unlike their approach, we
introduce semi-automatic synthesis based on general compile rules that
represent the common writing patterns to support future language updates and to
provide correct meaning of specification.  The extracted semantics via our tool
is also executable that helps to bridge gaps between the specification written
in a natural language and tests.

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in ECMAScript.  KJS~\cite{kjs} and
JaVerT~\cite{javert} defined formal semantics of JavaScript by manually converting
ECMAScript to their own formal languages.  KJS mapped
ES5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
However, all of them targets only ES5.1 or former versions of ECMAScript and
they do not provide solution for annual updates of ECMAScript. Our approach
provides a mechanized framework to synthesize JavaScript parsers and to
automatically extract semantics using a rule-based compilation technique, which
significantly reduces human efforts.

>>>>

From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
does not support context-sensitive features.  Unlike GLL parsing, our lookahead
parsing is applicable for JavaScript parsers with context sensitive features
such as positive/negative lookaheads. Moreover, the complexity of lookahead
parsing is \( O(k \cdot n) \) for the constant
number of tokens \( k \). We experimentally showed that it can generate parsers
for the most recent four versions of ECMAScript.

The closest work to ours in automatic model generation
is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and heuristic methods,
it produces candidate code and removes wrong ones
by testing them with actual implementation. Unlike their approach, we
introduce a semi-automatic synthesis using general compile rules that
represent common writing patterns of specifications.  The extracted
semantics by \(\tool\) is also executable, which allows to bridge gaps
between the specification written in a natural language and executable
tests.

Several approaches defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript expressing non-core
features using desugaring, but its correspondence with ECMAScript is
not obvious.
KJS~\cite{kjs} and JaVerT~\cite{javert} defined the JavaScript semantics
by manually converting ECMAScript to their own formal languages.  KJS mapped
ES5.1 in the K framework~\cite{kframework} and JaVerT converts the
specification to their own IR.  However, they all target only ES5.1 or former and
they do not provide any solution for annual updates of ECMAScript. Our approach
provides a mechanized framework to synthesize JavaScript parsers and to
automatically extract semantics using a rule-based compilation technique, which
significantly reduces human efforts.
